Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-06-15 doc/PRF2022/PRF_main.tex
updated figures

\begin{figure}
\begin{center}
  \includegraphics[width=0.24\textwidth]{Fig2a.png}
  \includegraphics[width=0.24\textwidth]{Fig2b.png}
  \includegraphics[width=0.24\textwidth]{Fig2c.png}
  \includegraphics[width=0.24\textwidth]{Fig2d.png}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 60 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.1\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
  \end{center}
\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1,0.2\}$. }
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.4\textwidth]{Nb198a.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198b.pdf}\\
  \includegraphics[width=0.4\textwidth]{Nb198c.pdf}
  \includegraphics[width=0.4\textwidth]{Nb198d.pdf}
\end{center}
\begin{caption}{\label{fig:relax}
  Panel (a) shows 60 particles confined to a square with random 
  positions and orientation.
  In a quiescent background flow, 
  the self-assembled particles take on distinct configurations
  depending on the value of the shift parameter $b$.}
\end{caption}
\end{figure}

@@

The equilibrium configurations for case (ii) and (iii) are used as initial data in the
background flow simulations found in Section \ref{sec:results}.
In case (i), there are several connected
components forming isolated bilayers, micelles, and vesicles (Figure~\ref{fig:relax}(b)).
To have a single, coherent vesicle (i), we reinitialize
the case (i) particles in the form of a ring and run the relaxation procedure once more.
\begin{figure}
  \begin{center}
  \includegraphics[width=0.5\textwidth]{Relax_Energy.jpg}\\
  \includegraphics[width=0.3\textwidth]{Nb60b.pdf}
  \includegraphics[width=0.3\textwidth]{Nb60c.pdf}
  \includegraphics[width=0.3\textwidth]{Nb60d.pdf}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax_energy}
    The free energy \eqref{eq:free_energy} is decreasing
    in the mobility problem formulation.  The initial energies
    are for the configuration in Figure \ref{fig:relax}a
    and the final energies are for the near-equilibrium
    configurations Figure \ref{fig:relax}b--c, respectively. 
    The red curves are the energies for the $N_b = 198$ cases normalized
    by $60/198$, showing that the energy approximately scales with the number of
    particles.
  }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VS_E.pdf}
   \includegraphics[width=0.3\textwidth]{VS_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VS_MSD.pdf}
  \end{center}
  \caption{
    \label{fig:BC1_shear}
    A vesicle in shear flows with shear rates $\dot\gamma=\{0.05, 0.0655, 0.075\}$. We propose the order parameter defined by $S_{loc} = \frac12(3\cos(\theta-\bar\theta)^2-1)$}
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.3\textwidth]{VTG_E.pdf}
   \includegraphics[width=0.3\textwidth]{VTG_LOP.pdf}
    \includegraphics[width=0.3\textwidth]{VTG_MSD.pdf}
  \end{center}
\caption{A vesicle in Taylor-Green flows when the flow strength $V_0=\{0.1, 0.15, 0.2\}$. }
\end{figure}
